Field-informed Reinforcement Learning for Learning Large-Scale Collective Tasks

### 2023-05-15 paper.tex
some comments
minors
minor

Autonomous agents interacting and operating towards a common task, rely on shared information and consequently emerging knowledge in order to achieve the underlying goals efficiently. Coordinating and organising this information exchange within the network of agents is required for improve the collaboration among them further~\cite{jennings1996coordination}. Through this coordination, agents may overcome problems requiring (i) efficiency and accuracy only achieved by multiple agents, (ii) the complimentary competences of the individual agents, or (iii) the collective resources of multiple agents.

@@

@@

  Compute the current expetected value for each node in the graph:
  $y^* = Q(s'i,a';\theta)$;

>>>>

Autonomous agents interacting and operating towards a common task, rely on shared information and consequently emerging knowledge in order to achieve the underlying goals efficiently. Coordinating and organising this information exchange within the network of agents is required for improve the collaboration among them further~\cite{jennings1996coordination}. Through this coordination, agents may overcome problems requiring (i) efficiency and accuracy only achieved by multiple agents, (ii) the complementary competences of the individual agents, or (iii) the collective resources of multiple agents.

@@

 \lukas{we have not introduced $G'_t$ yet}

@@

  Compute the current expected value for each node in the graph:
  $y^* = Q(s'i,a';\theta)$;
